Walk Through the Tutorial 4 of TikZ Manual

### 2019-12-22 mstemc/index.tex
the lecture map is OK and I am pretty satisfied with it

% Intended LaTeX compiler: pdflatex
\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
       \usepackage{tikz}
       \usetikzlibrary{arrows,decorations.pathmorphing}
       \usetikzlibrary{backgrounds,positioning,fit,petri}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{Walk Through the Tutorial 4 of TikZ Manual}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Walk Through the Tutorial 4 of TikZ Manual},
 pdfkeywords={},
 pdfsubject={Analyze the Elements Example in Chapter 3 of the TikZ manual line by line.},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/elements.pdf}
\end{center}
\end{document}

>>>>

% Intended LaTeX compiler: lualatex
\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{Walk Through the Tutorial 4 of TikZ Manual}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Walk Through the Tutorial 4 of TikZ Manual},
 pdfkeywords={},
 pdfsubject={Analyze the Elements Example in Chapter 3 of the TikZ manual line by line.},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/elements.pdf}
\end{center}
\section{Proposition II}
\label{sec:org3b99d67}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/propositionII.pdf}
\end{center}
\section{A Lecture Map Tutorial}
\label{sec:orgfae8e2b}

\begin{center}
\includegraphics[width=0.9\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/lecturemap.pdf}
\end{center}
\end{document}
